SST_patterns

### 2020-01-31 SST_patterns.Rmd
update

@@

Complete_mean_intensity <- rbind(CMC_binding,OISST_binding, G1SST_binding, MUR_binding) #%>% 
  #select(-heading, - distance, - lat, -lon)

# write.csv(Complete_mean_intensity ,'Complete_mean_intensity.csv') # Copied this and then removedsome columnss

Complete_mean_intensity2 <- Complete_mean_intensity2 %>% 
  select(-distance_km)

final_data <- rbind(Complete_mean_intensity2, SACTN_binding)
#write.csv(final_data,'final_data.csv')

final_intensity <- rbind(SACTN_mean_intensity, Complete_mean_intensity_)

>>>>

SACTN_upwell_base_ <- read_csv("Data/SACTN_upwell_base .csv") # The SACTN product column was added in

@@

Complete_mean_intensity <- rbind(CMC_binding,OISST_binding, G1SST_binding, MUR_binding) %>% 
  ungroup() %>% 
  select(-heading, - distance, -distance_km)

#write.csv(Complete_mean_intensity ,'Complete_mean_intensity.csv') # Copied this and then removedsome columnss

final_data <- rbind(Complete_mean_intensity, SACTN_binding)
# write.csv(final_data,'final_data.csv')
